---
name: Yena
surname: Kim
position: "Ph.D. student"
address: "University of Wisconsin-Madison"
phone: +1 608 695 8977
email: "yena.kim@wisc.edu"
github: Yenapolisci
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

I poisoned myself doing research.


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D. in Political Science", "2021-present", "University of Wisconsin-Madison", "Madison, WI",
  "M.A. in Political Science", "2021", "Yonsei University", "Seoul, Korea",
  "B.A. in Russian Language and Literature, Political Science and International Studies", "2017", "Yonsei University", "Seoul, Korea"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Research experience

Working Paper

“The Politics of UNESCO’s International Assistance Program in Authoritarian Regimes”, with Hyowon Lee and Whasun Jho

“The Dynamics of Trade Policy-Making in Authoritarian Regimes”, with Whasun Jho

“Cultural Diplomacy in International Relations”(Korean), with Whasun Jho

# Teaching experience
Lecturer, Spring 2021
Somyung Vision Classical Christian School
Seoul, Korea


Teaching Assistant(Graduate Courses)
Yonsei University

- International Political Economy, Professor Whasun Jho, Spring 2020 
- Case Studies of International Political Economy in East Asia, Professor Whasun Jho, Fall 2019
- Politics of Technology, Professor Whasun Jho, Spring 2019


Teaching Assistant(Undergraduate Courses)
Yonsei University 


- International Political Economy in East Asia, Professor Whasun Jho, Fall 2019 
- Social Network Politics, Professor Whasun Jho, Spring 2019 
- Principles of Macroeconomics, Professor Taejin Kim,  Fall 2013


# Awards and fellowships
University Graduate Fellowship


# Professional work experience
The Korean WEST Exchange Program Intern, Mar 2018 – Sep 2018
Girl Scouts of Central Texas
Austin, TX
 
Intern, Jun 2014 – Aug 2014\\
State Hermitage Museum 
Saint-Petersburg, Russia

Administrative Intern, Mar 2012\\
2012 Nuclear Security Summit Conference
Seoul, Korea

# Language and skills
Language: Korean, English, Russian



